A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies

### 2019-02-20 for_submission/rvaught_2018.tex
02/19/2018

\begin{document}
\title{A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies }
\author{Ryan Rickards Vaught}
\affiliation{Department of Astronomy, San Diego State University, San Diego, CA 92182, USA}
\affiliation{Department of Physics, University of California, San Diego, 9500 Gilman Dr., La Jolla, CA 92093, USA}

@@

\begin{abstract}
We perform a Very Large Telescope FOcal Reducer and low dispersion Spectrograph 2 (VLT/FORS2) narrowband imaging search around 5 star-forming galaxies at redshift $z=0.67-0.69$ in the Great Observatories Origins Deep Survey South (GOODS-S) field to constrain the radial extent of large-scale outflows traced by resonantly scattered \ion{Mg}{2} emission. The sample galaxies span star formation rates in the range $4\msunperyr< \mathrm{SFR} < 40\msunperyr$ and have stellar masses $9.9 \lesssim \log M_{*}/M_{\odot} \lesssim 11.0$, and exhibit outflows traced by \ion{Mg}{2} absorption with velocities $\sim150-420\mkms$.
These observations are uniquely sensitive, reaching surface brightness limits of 5.81 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ per 1 arcsec$^2$ aperture (at 5$\sigma$ significance).  We do not detect any extended emission around any of the sample galaxies, thus placing  upper limits on the brightness of extended \ion{Mg}{2} emission of $<6.51 \times 10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ at projected distances $R_{\perp} > 8-21$ kpc. The imaging also resolves the \ion{Mg}{2} absorption observed toward each galaxy spatially, revealing approximately constant absorption strengths across the galaxy disks. 
In concert with radiative transfer models predicting the surface brightness of \ion{Mg}{2} emission for a variety of simple wind morphologies, our detection limits suggest that either (1) the extent of the \ion{Mg}{2}-emitting material in the outflows from these galaxies is limited to $\lesssim 20$ kpc; or (2) the outflows are anisotropic and/or dusty.  
\end{abstract}

@@

The absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2}  with velocities $\sim150-420\mkms$ and equivalent widths (EW) $\sim 2-3$ \AA.  Modeling of the galaxy broad-band spectral energy distributions (SEDs) obtained from multi-wavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$. The properties of the sample, as well as precise target coordinates taken from \cite{Rubin_2014}, are listed in Table \ref{tab:prop}.

@@

\begin{figure*}[!ht]
\centering
\includegraphics[scale=.75]{fors2_color_imstamps.pdf}
\caption{Color imaging of our sample galaxies in the \emph{HST}/ACS F435W, F606W, and F775W filters obtained as part of the GOODS survey (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}). Each image is 5\arcsec $\times$ 5\arcsec\ (or about $35 \rm \ kpc \times 35 \rm \ kpc$).\label{fig:hstims}}
\end{figure*}

\begin{figure*}[!h]
\centering
\gridline{\fig{filt_26_spectra.pdf}{0.5\textwidth}{}
          \fig{filt_36_spectra.pdf}{0.5\textwidth}{}}
\gridline{\fig{filt_03_spectra.pdf}{0.5\textwidth}{}
          \fig{filt_64_spectra.pdf}{0.5\textwidth}{}}
           \fig{filt_57_spectra.pdf}{0.5\textwidth}{}
\caption{Keck/LRIS spectra of the sample galaxies and the transmission curves of the filters HeII+47 (blue dashed line) and HeII/3000+48 (red dashed line). The left-hand axis is in units of flux density and the right-hand axis is the percentage of light transmitted by the filter at each wavelength. Vertical dashed lines indicate the wavelengths of the redshifted \ion{Mg}{2}\ doublet. The \ion{Mg}{2}\ doublet falls fortuitously at the central wavelength of the HeII+47 filter for the galaxies shown in panels (a) through (d).}
\label{fig:spec_images}
\end{figure*}

\begin{figure}[h]
\centering
\includegraphics[scale=.55]{avg_seeing_HEII.pdf}
\includegraphics[scale=.55]{avg_seeing_HEII3000.pdf}
\caption{\emph{Top}: Distribution of seeing measurements for the 38 HeII+47 images.
\emph{Bottom}: Same for the HeII/3000+48 images. The median seeing value for the images in both filters is $\sim 0.8\arcsec$. 
The seeing conditions were calculated from DIMM measurements which are provided by ESO in the header of each science image.
\label{fig.seeing}}
\end{figure}

@@

\subsection{Image Reduction}
The imaging data were fully reduced using custom routines written in \emph{Python}. 
The images were first corrected by subtracting and removing the overscan region of the CCD. 
Then the images were bias-subtracted and flat-fielded using twilight flats.
%%% KHRR -- adjusting the following to be different from FAB's words
%To improve the flat-fielding essential for detecting faint extended emission across the %fields, we further correct for the illumination patterns using night-sky flats. The %night-sky flats were produced by combining the unregistered science frames with an %average sigma-clipping algorithm after masking out all the objects, and any bad pixels. 
%%%
An additional flat-fielding correction was performed using night-sky flats to improve our sensitivity to faint extended emission.  The night-sky flats were produced by first masking out all objects and bad pixels in the science frames, and then combining them using an average sigma-clipping algorithm.
Cosmic rays and bad pixels in the science images are removed by utilizing the \emph{L. A. Cosmic} algorithm \citep{Dokkum2001}.
The astrometry solutions were calculated via Astrometry.net \citep{Lang}, and yield a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$. Before image stacking, we ran each frame through \emph{SExtractor} \citeth{Bertin} to create a root mean square (RMS) map of each science image.

@@

\begin{deluxetable*}{c c c c D D c D}
\tablecaption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) includes both components of the \ion{Mg}{2} doublet and is 
determined from analysis of the supplemental Keck/LRIS spectra. \label{tab:prop}}
\tablehead{\colhead{Object} & \colhead{R.A.} & \colhead{Dec} & \colhead{$z$} & \multicolumn2c{$\log$(SFR)} & \multicolumn2c{$\log{(M)}$} & \colhead{EW$_{\rm{obs}}$} & \multicolumn2c{ $\tau_V$} \\ 
\colhead {} & \colhead {} & \colhead {} & \colhead{} & \multicolumn2c{($\log M_{\odot}$ yr$^{-1}$)} & \multicolumn2c{($\log{M_{*}/M_{\odot}}$)} & \colhead{(\AA)} & \multicolumn2c{}}
\decimals
\startdata
J033225.26-274524.0 (J.26)     & 03:32:25.26 & -27:45:23.9  &   0.6660  & $9.1_{-3.7}^{+1.3}$     & $9.86_{-0.04}^{+0.05}$   & \ $7.539\pm 0.354$   &  $1.227_{-0.20}^{+1.54}$ \\ 
J033231.36-274725.0 (J.36)     & 03:32:31.35 & -27:47:24.9  &   0.6669  & $10.5_{-1.6}^{+1.7}$   & $10.02_{-0.03}^{+0.03}$ & \ $5.835 \pm 0.493$   & $1.377_{-0.23}^{+0.60}$ \\
J033230.03-274347.3 (J.03)     & 03:32:30.03 & -27:43:47.2  &   0.6679  & $3.8_{-0}^{+0}$           & $10.98_{-0.0}^{+0.01}$   & $12.794 \pm 1.710$ & $0.297_{-0.0}^{+0.0}$ \\
J033229.64-274242.6 (J.64)     & 03:32:29.64 & -27:42:42.5  &   0.6671  & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ & $13.239 \pm 0.263$ & $3.897_{-0.93}^{+1.15}$ \\
J033230.57-274518.2 (J.57)     & 03:32:30.56 & -27:45:18.2  &   0.6807  & $12.6_{-2.1}^{+1.7}$   & $10.48_{-0.07}^{+0.03}$ & \ $6.106 \pm 0.370$   & $1.262_{-0.40}^{+1.23}$ \\
\enddata
\tablecomments{The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}.}
\end{deluxetable*}

\begin{deluxetable}{c c c c c c}
\tablecaption{Filter properties  and exposure times of the VLT/FORS2 observations. The widths of the transmission curves ($\Delta\lambda$) are calculated by convolving the transmission curves over the total wavelength range of each filter. 
%These values differ slightly from those reported by the European Southern Observatory.
 \label{tab:filters}}
\tablehead{\colhead {Filter (Line)} & \colhead {$\lambda_{\rm{eff}}$\tablenotemark{a}} & \colhead {$\Delta\lambda$\tablenotemark{b}} & \colhead {N\tablenotemark{c}} & \colhead{$T$\tablenotemark{d}} & \colhead{$S$\tablenotemark{e}} \\
\colhead {} & \colhead{(\AA)} & \colhead{(\AA)} & \colhead{} & \colhead{(sec)} & \colhead{}}
\startdata
HeII+47 (\ion{Mg}{2})         & 4675.21  & 50.11 & 38  & 35,959 & 2.45 \\
HeII/3000+48 (Cont.) & 4722.46  & 44.82 & 38  & 36,937 & 2.40  \\
\enddata
\tablenotetext{a}{$ \lambda_{\rm{eff}}$ is the effective wavelength of the filter transmission curve.}
\tablenotetext{b}{FWHM of the filter.}
\tablenotetext{c}{Total number of images.}
\tablenotetext{d}{Total exposure time.}
\tablenotetext{e}{S, the sensitivity of the filter, is in units of $10^{-17}$ ergs counts$^{-1}$ cm$^{-2}$.}
\end{deluxetable}\ 
%\\

@@

\begin{figure*}[ht!]
\centering
\includegraphics[scale=.61]{HEII_final.png}
\includegraphics[scale=.61]{HEII3000_final.png}
\caption{\emph{Top:} Stacked HeII+47 image of the galaxy sample. \emph{Bottom:} Stacked HeII3000+48 image of the same pointing. The exposure time of each image is $\approx 10$ hours. Each image shows approximately half of the total FORS2 FOV ($7' \times 5'$), which contains the full sample of galaxies (indicated by the white arrows). East is up and North is right.
\label{fig:stacked_image}}
\end{figure*}

@@

Comparing these ratios between each galaxy, we find that they are equivalent to within 0.1\%, with a value of 1.118. This value is equal to the ratio between the FWHMs of the filter transmission curves, indicating that the spectral slope of each galaxy is approximately flat, and that the continuum level measured in the off-line filter provides an accurate measure of the continuum contribution to the on-line filter flux.  We thus do not apply any spectral correction in the following analysis.

@@

To properly continuum-subtract the image taken with the \ion{Mg}{2} filter, we follow a prescription given by \cite{Battaia_2015}. 
We first determine the continuum flux density from the continuum filter,
\begin{equation}
f_{\rm{cont}}=\frac{F_{\rm{cont}}}{\Delta \lambda_{\rm{cont}}},
\end{equation}\\
where $F_{\rm{cont}}$ and $\Delta \lambda_{\rm{cont}}$ are the observed flux per pixel of the continuum image and the transmission FWHM of the continuum filter, respectively. With $f_{\rm cont}$ it is then possible to calculate the flux of any excess emission, $F_{\rm{line}}$:
\begin{equation}
F_{\rm{line}}=F_{\rm{MgII}}-f_{\rm{cont}} \Delta \lambda_{\rm{MgII}}
\label{eq:subtraction}
\end{equation}
where $F_{\rm{MgII}}$ and $\Delta \lambda_{\rm MgII}$ are the observed flux per pixel in the \ion{Mg}{2} filter and the transmission FWHM of the \ion{Mg}{2} filter. The continuum-subtracted images of each galaxy are shown in Figure \ref{fig:stamp_images}. %The continuum-subtracted 
These
images have a uniform background and no obvious signatures of emission.

\begin{figure*}[!htb]
\centering
\includegraphics[scale=0.7]{stamps.pdf}
\caption{ $10'' \times 10''$ (or about $70 \rm \ kpc \times 70 \rm \ kpc $) images of each galaxy in our sample. Top row: Continuum surface brightness in ergs s$^{-1}$ cm$^{-2}$ pixel, measured in the HeII/3000+48 filter. Bottom row: Continuum-subtracted \ion{Mg}{2} surface brightness.  Absorption can be seen in 4 of 5 galaxies. The red contours represent the outline of the 1$\sigma$ surface brightness limit in the HeII+47 image, defined in Sec. \ref{sec.sb}. The colorbar shows the scaling used for the \ion{Mg}{2} images in the bottom row.}
\label{fig:stamp_images}
\end{figure*}

@@

\begin{figure*}
\centering
\gridline{\fig{J_26.pdf}{0.5\textwidth}{}
          \fig{J_36.pdf}{0.5\textwidth}{}}
\gridline{\fig{J_03.pdf}{0.5\textwidth}{}
          \fig{J_64.pdf}{0.5\textwidth}{}}
           \fig{J_57.pdf}{0.5\textwidth}{}
\caption{SB profiles for our sample galaxies. Top panels: Continuum SB profile (gray) measured for each galaxy. The red points show the Mg II + continuum SB measured for the galaxy in the pre-continuum-subtracted line image. The blue points show the Mg II line SB measured  in the continuum-subtracted line emission image.  The profile exhibits SB decrements from \ion{Mg}{2} absorption. Photometry was performed in circular annuli. Bottom panel: The vertical hashes show the inner and outer radii of each annulus in kpc. The distance from the center of the galaxy is marked with filled squares and is computed using the average value of the inner and outer radii of each annulus.}
\label{fig:sb_profiles}
\end{figure*}

@@

In the case of perfect sky subtraction and continuum subtraction, the 1$\sigma$ SB limit for an extended source is $SB_{1}/\sqrt{A_\text{src}}$, where $A_\text{src}$ is the area in arcsec$^2$ and $SB_{1}$ is the surface brightness limit per 1 arcsec$^2$ aperture. However, our actual detection limits are altered by systematic errors from imperfect subtraction. Therefore, we determine the limits as follows. 
We first mask all the artifacts and sources in the continuum-subtracted images. Next, we generate many apertures with sizes similar to our extended annuli ($\sim 20 \rm\ sq.arcsec$), place them at random, and extract the fluxes, $F_{\text{src}}$, within these apertures. We then normalize the values of $F_{\text{src}}$ by dividing by $\sigma_{\text{src}}$, where $\sigma_{\text{src}} \equiv SB_{1}\sqrt{A_\text{src}}$. For perfect sky subtraction and continuum subtraction, the distribution of extracted fluxes should follow a Gaussian distribution with a variance equal to $\sigma_{\text{src}}$. The distribution of $F_{\text{src}}/\sigma_{\text{src}}$ for these apertures is shown in Figure \ref{fig:limits}

We calculate the variance and mean of the distribution and find that the variance of the distribution is $\sigma'_{\text{src}}=1.1$, implying that the SB detection limit for our continuum-subtracted image is higher than $\sigma_{\text{src}}$ by a factor of 10\%. We adopt $F_{\text{limit}} \equiv \sigma'_{\text{src}}$  as the $1 \sigma$ upper limit on the total line flux of extended \ion{Mg}{2} emission. The SB$_{\text{limit}}$ is then $F_{\text{limit}}/A_{\rm{src}}$. The values of $F_{\text{src}}$ and 5SB$_{\text{limit}}$ for each galaxy are listed in Table \ref{tab:det_lims}.

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.6]{hist_sblim.pdf}
\caption{Normalized distribution of $F_{\text{src}}/\sigma_{\text{src}}$ values for random circular annuli placed on the continuum-subtracted line image. $F_{\text{src}}$ is the total flux within an aperture and $\sigma_{\text{src}}$ is the expected $1\sigma$ flux limit in the ideal case of perfect sky and continuum subtraction, i.e $SB_{1}\sqrt{A_\text{src}}$. The black arrows point to the statistical significance of the flux inside the ``extended annulus'' of each galaxy.}
\label{fig:limits}
\end{figure}

@@

\begin{figure*}[p]
\centering
\includegraphics[scale=1.2]{sigmas.pdf}
\caption{Continuum-subtracted $\chi_{\text{smooth}}$ images of the 5 galaxies in our sample. Every galaxy is placed in the same row in each column. The columns show simulated emission, with brightnesses of 0, 1, 3, 5, 10, and 20 times SB$_{\rm lim}$.  Each image has a size of $5'' \times 5''$ (corresponding to $35$ kpc $\times$ $35$ kpc at $z\sim 0.70$). Each image shows the galaxy along with the same isophotal contour used in previous figures (in black).}
\label{fig:sigmas}
\end{figure*}

>>>>

\begin{document}
\title{A VLT/FORS2 Narrowband Imaging Search for \ion{Mg}{2} Emission Around $\lowercase{z}\sim0.7$ Galaxies }
\author{Ryan Rickards Vaught}
\affiliation{Department of Physics, University of California, San Diego, 9500 Gilman Dr., La Jolla, CA 92093, USA}
\affiliation{Department of Astronomy, San Diego State University, San Diego, CA 92182, USA}

@@

\begin{abstract}
We perform a Very Large Telescope FOcal Reducer and low dispersion Spectrograph 2 (VLT/FORS2) narrowband imaging search around 5 star-forming galaxies at redshift $z=0.67-0.69$ in the Great Observatories Origins Deep Survey South (GOODS-S) field to constrain the radial extent of large-scale outflows traced by resonantly scattered \ion{Mg}{2} emission. The sample galaxies span star formation rates in the range $4\msunperyr< \mathrm{SFR} < 40\msunperyr$ and have stellar masses $9.9 \lesssim \log M_{*}/M_{\odot} \lesssim 11.0$, and exhibit outflows traced by \ion{Mg}{2} absorption with velocities $\sim150-420\mkms$.
These observations are uniquely sensitive, reaching surface brightness limits of 5.81 $\times$ $10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ per 1 arcsec$^2$ aperture (at 5$\sigma$ significance).  We do not detect any extended emission around any of the sample galaxies, thus placing 5$\sigma$ upper limits on the brightness of extended \ion{Mg}{2} emission of $<6.51 \times 10^{-19}$ ergs sec $^{-1}$ cm$^{-2}$ arcsec$^2$ at projected distances $R_{\perp} > 8-21$ kpc. The imaging also resolves the \ion{Mg}{2} absorption observed toward each galaxy spatially, revealing approximately constant absorption strengths across the galaxy disks. 
In concert with radiative transfer models predicting the surface brightness of \ion{Mg}{2} emission for a variety of simple wind morphologies, our detection limits suggest that either (1) the extent of the \ion{Mg}{2}-emitting material in the outflows from these galaxies is limited to $\lesssim 20$ kpc; or (2) the outflows are anisotropic and/or dusty.  
\end{abstract}

@@

The absorption line modeling presented in \cite{Rubin_2014} indicates that these five galaxies are driving strong outflows traced by \ion{Mg}{2}  with velocities $\sim150-420\mkms$ and \textbf{rest-frame} equivalent widths (EW) $\sim 2-3$ \AA.  Modeling of the galaxy broad-band spectral energy distributions (SEDs) obtained from multi-wavelength ancillary imaging data yields star formation rates (SFR) ranging from $\sim4$ to $40\msunperyr$ and stellar masses in the range $\log M_*/M_{\odot}\sim 9.9-11.0$. The properties of the sample, as well as precise target coordinates taken from \cite{Rubin_2014}, are listed in Table \ref{tab:prop}.

@@

\begin{figure*}[!ht]
\centering
\includegraphics[scale=.75]{figure1.pdf}%fors2_color_imstamps.pdf%%
\caption{Color imaging of our sample galaxies in the \emph{HST}/ACS F435W, F606W, and F775W filters obtained as part of the GOODS survey (\citeauthor{Giavalisco2004} \citeyear{Giavalisco2004}). Each image is 5\arcsec $\times$ 5\arcsec\ (or about $35 \rm \ kpc \times 35 \rm \ kpc$).\label{fig:hstims}}
\end{figure*}

\begin{figure*}[!h]
\centering
\gridline{\fig{figure2a.pdf}{0.5\textwidth}{}
          \fig{figure2b.pdf}{0.5\textwidth}{}}
\gridline{\fig{figure2c.pdf}{0.5\textwidth}{}
          \fig{figure2d.pdf}{0.5\textwidth}{}}
         \fig{figure2e.pdf}{0.5\textwidth}{}
\caption{Keck/LRIS spectra of the sample galaxies and the transmission curves of the filters HeII+47 (blue dashed line) and HeII/3000+48 (red dashed line). The left-hand axis is in units of flux density and the right-hand axis is the percentage of light transmitted by the filter at each wavelength. Vertical dashed lines indicate the wavelengths of the redshifted \ion{Mg}{2}\ doublet. The \ion{Mg}{2}\ doublet falls fortuitously at the central wavelength of the HeII+47 filter for the galaxies shown in panels (a) through (d).}
\label{fig:spec_images}
\end{figure*}

\begin{figure}[h]
\centering
\includegraphics[scale=.55]{figure3a.pdf}
\includegraphics[scale=.55]{figure3b.pdf}
\caption{\emph{Top}: Distribution of seeing measurements for the 38 HeII+47 images.
\emph{Bottom}: Same for the HeII/3000+48 images. The median seeing value for the images in both filters is $\sim 0.8\arcsec$. 
The seeing conditions were calculated from DIMM measurements which are provided by ESO in the header of each science image.
\label{fig.seeing}}
\end{figure}

@@

\subsection{Image Reduction}
The imaging data were fully reduced using custom routines written in \emph{Python}. 
The images were first corrected by subtracting and removing the overscan region of the CCD. 
Then the images were bias-subtracted and flat-fielded using twilight flats.
An additional flat-fielding correction was performed using night-sky flats to improve our sensitivity to faint extended emission.  The night-sky flats were produced by first masking out all objects and bad pixels in the science frames, and then combining them using an average sigma-clipping algorithm.
Cosmic rays and bad pixels in the science images are removed by utilizing the \emph{L. A. Cosmic} algorithm \citep{Dokkum2001}.
The astrometry solutions were calculated via Astrometry.net \citep{Lang}, and yield a standard deviation in the galaxy coordinates of $\sigma \approx 0.10''$. Before image stacking, we ran each frame through \emph{SExtractor} \citeth{Bertin} to create a root mean square (RMS) map of each science image.

@@

\begin{deluxetable*}{c c c c D D c D}
\tablecaption{Properties of the 5 galaxies in our sample as estimated in \cite{Rubin_2014}. The EW (in the observed frame) includes both components of the \ion{Mg}{2} doublet and is 
determined from analysis of the supplemental Keck/LRIS spectra. \label{tab:prop}}
\tablehead{\colhead{Object} & \colhead{R.A.} & \colhead{Dec} & \colhead{$z$} & \multicolumn2c{SFR} & \multicolumn2c{$\log{(M)}$} & \colhead{EW$_{\rm{obs}}$} & \multicolumn2c{ $\tau_V$} \\ 
\colhead {} & \colhead {} & \colhead {} & \colhead{} & \multicolumn2c{($M_{\odot}$ yr$^{-1}$)} & \multicolumn2c{($\log{M_{*}/M_{\odot}}$)} & \colhead{(\AA)} & \multicolumn2c{}}
\decimals
\startdata
J033225.26-274524.0 (J.26)     & 03:32:25.26 & -27:45:23.9  &   0.6660  & $9.1_{-3.7}^{+1.3}$     & $9.86_{-0.04}^{+0.05}$   & \ $7.5\pm 0.4$   &  $1.227_{-0.20}^{+1.54}$ \\ 
J033231.36-274725.0 (J.36)     & 03:32:31.35 & -27:47:24.9  &   0.6669  & $10.5_{-1.6}^{+1.7}$   & $10.02_{-0.03}^{+0.03}$ & \ $5.8 \pm 0.5$   & $1.377_{-0.23}^{+0.60}$ \\
J033230.03-274347.3 (J.03)     & 03:32:30.03 & -27:43:47.2  &   0.6679  & $3.8_{-0}^{+0}$           & $10.98_{-0.0}^{+0.01}$   & $12.8 \pm 1.7$ & $0.297_{-0.0}^{+0.0}$ \\
J033229.64-274242.6 (J.64)     & 03:32:29.64 & -27:42:42.5  &   0.6671  & $40.5_{-12.1}^{+8.2}$ & $10.30_{-0.03}^{+0.07}$ & $13.2 \pm 0.3$ & $3.897_{-0.93}^{+1.15}$ \\
J033230.57-274518.2 (J.57)     & 03:32:30.56 & -27:45:18.2  &   0.6807  & $12.6_{-2.1}^{+1.7}$   & $10.48_{-0.07}^{+0.03}$ & \ $6.1 \pm 0.4$   & $1.262_{-0.40}^{+1.23}$ \\
\enddata
\tablecomments{The uncertainty intervals reported for SFR, $\log M_*/M_{\odot}$, and $\tau_V$ i.e. \textbf{dust opacity of the galaxy}, values indicate the $\pm34$th-percentile values of the posterior probability distribution function of each quantity as determined via modeling of the objects' SEDs with MAGPHYS (\citeauthor{daCunha2008} \citeyear{daCunha2008}, \citeyear{daCunha2012}) as described in \citet{Rubin_2014}.}
\end{deluxetable*}

\begin{deluxetable}{c c c c c c}
\tablecaption{Filter properties  and exposure times of the VLT/FORS2 observations. The widths of the transmission curves ($\Delta\lambda$) are calculated by convolving the transmission curves over the total wavelength range of each filter. 
%These values differ slightly from those reported by the European Southern Observatory.
 \label{tab:filters}}
\tablehead{\colhead {Filter (Line)} & \colhead {$\lambda_{\rm{eff}}$\tablenotemark{a}} & \colhead {$\Delta\lambda$\tablenotemark{b}} & \colhead {N\tablenotemark{c}} & \colhead{$T$\tablenotemark{d}} & \colhead{$S$\tablenotemark{e}} \\
\colhead {} & \colhead{(\AA)} & \colhead{(\AA)} & \colhead{} & \colhead{(sec)} & \colhead{}}
\startdata
HeII+47 (\ion{Mg}{2})         & 4675.21  & 50.11 & 38  & 35,959 & 2.45 \\
HeII/3000+48 (Cont.) & 4722.46  & 44.82 & 38  & 36,937 & 2.40  \\
\enddata
\tablenotetext{a}{$ \lambda_{\rm{eff}}$ is the effective wavelength of the filter transmission curve.}
\tablenotetext{b}{The effective width of the filter.}
\tablenotetext{c}{Total number of images.}
\tablenotetext{d}{Total exposure time.}
\tablenotetext{e}{S, the sensitivity of the filter, is in units of $10^{-17}$ ergs counts$^{-1}$ cm$^{-2}$.}
\end{deluxetable}\ 
%\\

@@

\begin{figure*}[ht!]
\centering
\includegraphics[scale=.61]{figure4a.pdf}
\includegraphics[scale=.61]{figure4b.pdf}
\caption{\emph{Top:} Stacked HeII+47 image of the galaxy sample. \emph{Bottom:} Stacked HeII3000+48 image of the same pointing. The exposure time of each image is $\approx 10$ hours. Each image shows approximately half of the total FORS2 FOV ($7' \times 5'$), which contains the full sample of galaxies (indicated by the white arrows). East is up and North is right.
\label{fig:stacked_image}}
\end{figure*}

@@

Comparing these ratios between each galaxy, we find that they are equivalent to within 0.1\%, with a value of 1.118. This value is equal to the ratio between the effective widths of the filter transmission curves, indicating that the spectral slope of each galaxy is approximately flat, and that the continuum level measured in the off-line filter provides an accurate measure of the continuum contribution to the on-line filter flux.  We thus do not apply any spectral correction in the following analysis.

@@

To properly continuum-subtract the image taken with the \ion{Mg}{2} filter, we follow a prescription given by \cite{Battaia_2015}. 
We first determine the continuum flux density from the continuum filter,
\begin{equation}
f_{\rm{cont}}=\frac{F_{\rm{cont}}}{\Delta \lambda_{\rm{cont}}},
\end{equation}\\
where $F_{\rm{cont}}$ and $\Delta \lambda_{\rm{cont}}$ are the observed flux per pixel of the continuum image and the effective width of the continuum filter, respectively. With $f_{\rm cont}$ it is then possible to calculate the flux of any excess emission, $F_{\rm{line}}$:
\begin{equation}
F_{\rm{line}}=F_{\rm{MgII}}-f_{\rm{cont}} \Delta \lambda_{\rm{MgII}}
\label{eq:subtraction}
\end{equation}
where $F_{\rm{MgII}}$ and $\Delta \lambda_{\rm MgII}$ are the observed flux per pixel in the \ion{Mg}{2} filter and the effective width of the \ion{Mg}{2} filter. The continuum-subtracted images of each galaxy are shown in Figure \ref{fig:stamp_images}. %The continuum-subtracted 
These
images have a uniform background and no obvious signatures of emission.

\begin{figure*}[!htb]
\centering
\includegraphics[scale=0.7]{figure5.pdf}%stamps.pdf
\caption{ $10'' \times 10''$ (or about $70 \rm \ kpc \times 70 \rm \ kpc $) images of each galaxy in our sample. Top row: Continuum surface brightness in ergs s$^{-1}$ cm$^{-2}$ pixel, measured in the HeII/3000+48 filter. Bottom row: Continuum-subtracted \ion{Mg}{2} surface brightness.  Absorption can be seen in 4 of 5 galaxies. The red contours represent the outline of the 1$\sigma$ surface brightness limit in the HeII+47 image, defined in Sec. \ref{sec.sb}. The colorbar shows the scaling used for the \ion{Mg}{2} images in the bottom row.}
\label{fig:stamp_images}
\end{figure*}

@@

\begin{figure*}
\centering
\gridline{\fig{figure6a.pdf}{0.5\textwidth}{}
          \fig{figure6b.pdf}{0.5\textwidth}{}}
\gridline{\fig{figure6c.pdf}{0.5\textwidth}{}
          \fig{figure6d.pdf}{0.5\textwidth}{}}
           \fig{figure6e.pdf}{0.5\textwidth}{}
\caption{SB profiles for our sample galaxies. Top panels: Continuum SB profile (gray) measured for each galaxy. The red points show the Mg II + continuum SB measured for the galaxy in the pre-continuum-subtracted line image. The blue points show the Mg II line SB measured  in the continuum-subtracted line emission image.  The profile exhibits SB decrements from \ion{Mg}{2} absorption. Photometry was performed in circular annuli. Bottom panel: The vertical hashes show the inner and outer radii of each annulus in kpc. The distance from the center of the galaxy is marked with filled squares and is computed using the average value of the inner and outer radii of each annulus. The annuli with the largest radial distance from the galaxy are used to measure extended SBs.}
\label{fig:sb_profiles}
\end{figure*}

@@

In the case of perfect sky subtraction and continuum subtraction, the 1$\sigma$ SB limit for an extended source is $SB_{1}/\sqrt{A_\text{src}}$, where $A_\text{src}$ is the area in arcsec$^2$ and $SB_{1}$ is the surface brightness limit per 1 arcsec$^2$ aperture. However, our actual detection limits are altered by systematic errors from imperfect subtraction. Therefore, we determine the limits as follows. 
We first mask all the artifacts and sources in the continuum-subtracted images. Next, we generate many apertures with sizes similar to our extended annuli ($\sim 20 \rm\ sq.arcsec$), place them at random, and extract the fluxes, $F_{\text{src}}$, within these apertures. We then normalize the values of $F_{\text{src}}$ by dividing by $\sigma_{\text{src}}$, where $\sigma_{\text{src}} \equiv SB_{1}\sqrt{A_\text{src}}$. For perfect sky subtraction and continuum subtraction, the distribution of extracted fluxes should follow a Gaussian distribution with a standard deviation equal to $\sigma_{\text{src}}$. The distribution of $F_{\text{src}}/\sigma_{\text{src}}$ for these apertures is shown in Figure \ref{fig:limits}

We calculate the standard deviation and mean of the distribution and find that the variance of the distribution is $\sigma'_{\text{src}}=1.1$, implying that the SB detection limit for our continuum-subtracted image is higher than $\sigma_{\text{src}}$ by a factor of 10\%. We adopt $F_{\text{limit}} \equiv \sigma'_{\text{src}}$  as the $1 \sigma$ upper limit on the total line flux of extended \ion{Mg}{2} emission. The SB$_{\text{limit}}$ is then $F_{\text{limit}}/A_{\rm{src}}$. The values of $F_{\text{src}}$ and 5SB$_{\text{limit}}$ for each galaxy are listed in Table \ref{tab:det_lims}.

\begin{figure}[!ht]
\centering
\includegraphics[scale=0.6]{figure7.pdf}%hist_sblim
\caption{Normalized distribution of $F_{\text{src}}/\sigma_{\text{src}}$ values for random circular annuli placed on the continuum-subtracted line image. $F_{\text{src}}$ is the total flux within an aperture and $\sigma_{\text{src}}$ is the expected $1\sigma$ flux limit in the ideal case of perfect sky and continuum subtraction, i.e $SB_{1}\sqrt{A_\text{src}}$. The red line is a Gaussian fit to this normalized distribution with standard deviation, $\sigma=1.112$, and mean, $\mu=-0.441$. The black arrows point to the statistical significance of the flux inside the ``extended annulus'' of each galaxy.}
\label{fig:limits}
\end{figure}

@@

\begin{figure*}[p]
\centering
\includegraphics[scale=1.2]{figure8.pdf}%sigmas.pdf
\caption{Continuum-subtracted $\chi_{\text{smooth}}$ images of the 5 galaxies in our sample. Every galaxy is placed in the same row in each column. The columns show simulated emission, with brightnesses of 0, 1, 3, 5, 10, and 20 times SB$_{\rm lim}$.  Each image has a size of $5'' \times 5''$ (corresponding to $35$ kpc $\times$ $35$ kpc at $z\sim 0.70$). Each image shows the galaxy along with the same isophotal contour used in previous figures (in black).}
\label{fig:sigmas}
\end{figure*}
